---
title: "Application of quanteda: Chinese"
date: "2017-04-20"
author: Haiyan Wang
output:
  md_document:
    variant: markdown_github
---

# Application of quanteda: Chinese
### _Haiyan Wang_


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Chinese Stop words: Baidu Stopwords
```{r}
require(readtext)
require(stringi)
require(quanteda)

#read Chinese stop words
csw <- readtext("ChineseStopWords.txt")
csw <- unlist(as.list(tokens(csw$text, remove_punct=T)))

# an example of using csw
removeFeatures(tokens("中华人民共和国成立于1949 年"), csw)
```

## Example application on a set of text files in Chinese

49 "REPORT ON THE WORK OF THE GOVERNMENT" by Premier of the State Council, 1954 - 2017 
```{r}
#read text files
ctxt<-readtext("govReports/*.txt")

#create corpus
chCorpus <- corpus(ctxt)
summary(chCorpus)

#tokenize
chtoks <- tokens(ctxt$text, remove_punct = TRUE)
chtoks <- removeFeatures(chtoks, csw)

#dfm
chdfm <- dfm(chtoks)
topfeatures(chdfm)
#发展 经济 社会 建设 改革 人民 主义 工作 企业 国家 
#5627 5036 4255 4248 2931 2897 2817 2642 2627 2595 

# plot a word cloud
set.seed(100)
chdfm_tf <- dfm_trim(chdfm, min_count = 500)
if(Sys.info()['sysname'] == "Darwin"){ # Mac...
  par(family = "STSong") 
}
textplot_wordcloud(chdfm_tf, min.freq = 6, random.order = FALSE,
                   rot.per = .25, 
                   colors = RColorBrewer::brewer.pal(8,"Dark2"))
```

### Feature co-occurrence matrix
```{r}
#fcm within the same ducuments
ch17txt <- readtext("govReports/2017*.txt")
ch17toks <- tokens(ch17txt$text, remove_punct = TRUE)
ch17toks <- removeFeatures(ch17toks, csw)
chfcm <- fcm(ch17toks)

#fcm within window
chfcm <- fcm(ch17toks, context = "window")  # default window size = 5
topfeatures(chfcm["改革", ])

# fcm within window: "改革"+ “xx”
chfcm <- fcm(ch17toks, context = "window", ordered = TRUE, tri = FALSE)  # default window size = 5
topfeatures(chfcm["改革", ])
```

### Scaling Model
```{r}
wfm <- textmodel_wordfish(chdfm)
y <- 1954:2017
y<-y[-which(y==1963 | y==1961 |y==1962 | (y>1964 & y<1975) | y==1976 |y==1977)]
plot(y, wfm@theta, xlab = "Year", ylab = "Position")
```

## Issues: English version vs. Chinese version
```{r}
en17txt <- readtext("ch_gov_report-2017.txt")
en17toks <- tokens(en17txt$text, remove_punct = TRUE)
en17toks <- removeFeatures(en17toks, stopwords(kind = "english"))

topfeatures(dfm(ch17toks))
topfeatures(dfm(en17toks))
```

### Segmentation issues
```{r}
head(kwic(ch17toks, "性", window = 3))
```

供给 侧 结构 | 性 | 改革 初 成效  initial success was achieved in supply-side structural reform.

### Translation issues
China： 我国 我们 国内 国家 全国....
